---
title: "Assignment 5"
author: "Wanjiku Ngare"
date: "10/8/2020"
output: html_document
---

```{r}
library(tidyverse)
library(jtools)
library(interactions)
library(knitr)
```

```{r}
person_data2 <- read_csv("people3.csv") %>%
   mutate(PAOC_label = case_when(
    PAOC_label== "Females with no own children"~"1No children",
     PAOC_label== "Females with own children 6 to 17 years only"~"Older Children",
    PAOC_label== "Females with own children under 6 years and 6 to 17 years"~"Both Children",
    PAOC_label=="Females with own children under 6 years only"~"Younger Children"))%>%
   
  mutate(marriage_status = case_when(
    MAR = 
    MAR == 1 ~ "Married",

    MAR == 2 ~ "Widowed",

    MAR == 3 ~ "Divorced",

    MAR == 4 ~ "Separated",

    MAR == 5 ~ "1Never married"))%>%
  
select(marriage_status, PAOC_label, PAP, PINCP) 
```

*Initial Regression Model*

_For this linear regression, I am testing how much years married, number of children (PAOC_label), and income (PINCP) impact public assistance income received in the past 12 months (PAP)._

In this version of the regression model, I took out the 'negative' and 'zero' income values from my people csv, reducing my data  points form 7,294 to 5,869 observations total. The reason I did this was so that I could actually complete the log transformation in model2.

```{r}
model1 <- lm(PAP ~ marriage_status + PINCP + PAOC_label,
            data = person_data2)

summary(model1)
```

With a multipe r-squared of 0.1163, the above independent  variables explain approximately 11.63% of  the dependent variable, public assistance income received in the last 12-months. With respect to the dependent variable of 'receiving public assistance in the last 12 months (PAP) and with a comparative variable of 'No children', four independent variables appear to be significant: at a 99% confidence interval - Income, Having Both  children (older and younger; at a 95% confidence interval - Having Older Children and Having Younger Children. 

*A log transformation*

```{r}
model2 <- lm(PAP ~ marriage_status + log(PINCP) + PAOC_label,
            data = person_data2)

summary(model2)
```

A

```{r}
model3 <- lm(PAP ~ marriage_status + log(PINCP) + PAOC_label +
               log(PINCP):PAOC_label + marriage_status:PAOC_label,
            data = person_data2)

summary(model3)
```


```{r}
ModelFit <- tibble(model = c(1, 2, 3),
                   R_square = c(summary(model1)$adj.r.squared,
                                summary(model2)$adj.r.squared,
                                summary(model3)$adj.r.squared))

ggplot(ModelFit, aes(x = model, y = R_square)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 4, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "Adjusted R-squared value") +
  theme_bw()
```

In this case, Model 3 appears to be the best fit

Try number 1: I I'm getting an error that I can't seem to figure out
```{r}
coeff_names <- c("Marriage status\n(compared to never married)" = "marriage_status",
                 "Annual income" = 
                   "PINCP",
                 "Annual income\n(log-transformed)" = 
                   "log(PINCP)",
                 "Own children\n(compared to no children)" = "PAOC_label",
                "Interaction:\nOlder Children and log-transformed income"="log(PINCP):PAOC_labelOlder children",
                "Interaction:\nYounger Children and log-transformed income"="log(PINCP):PAOC_labelYounger children",
                "Interaction:\nDivorced and Both Children" = "marriage_statusDivorced:PAOC_labelBoth children",
                "Interaction:\nMarried and Both Children" = "marriage_statusMarried:PAOC_labelBoth children",
                "Interaction:\nSeparated and Both Children" = "marriage_statusSeparated:PAOC_labelBoth children",
                "Interaction:\nWidowed and Both Children" = "marriage_statusWidowed:PAOC_labelBoth children",
                "Interaction:\nDivorced and Older Children" = "marriage_statusDivorced:PAOC_labelOlder children",
                "Interaction:\nMarried and Older Children" = "marriage_statusMarried:PAOC_labelOlder children",
                "Interaction:\nSeparated and Older Children" = "marriage_statusSeparated:PAOC_labelOlder children",
                "Interaction:\nWidowed and Older Children" = "marriage_statusWidowed:PAOC_labelOlder children",
                "Interaction:\nDivorced and Younger Children" = "marriage_statusDivorced:PAOC_labelYounger children",
                "Interaction:\nMarried and Younger Children" = "marriage_statusMarried:PAOC_labelYounger children",
                "Interaction:\nSeparated and Younger Children" = "marriage_statusSeparated:PAOC_labelYounger children",
                "Interaction:\nSeparated and Younger Children" = "marriage_statusWidowed:PAOC_labelYounger children")

export_summs(model1, model3, 
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial model", "Preferred model"),
             coefs = coeff_names)
```
Try number 2: I attempted to edit the code and still got the same error
```{r}
coeff_names <- c("Divorced\n(compared to never married)" = "marriage_statusDivorced",
                 "Married\n(compared to never married)" = "marriage_statusMarried",
                 "Separated\n(compared to never married)" = "marriage_statusSeparated",
                 "Widowed\n(compared to never married)" = "marriage_statusWidowed",
                 "Annual income" = 
                   "PINCP",
                 "Annual income\n(log-transformed)" = 
                   "log(PINCP)",
                 "Own children Both\n(compared to no children)" = "PAOC_labelBoth children",
                 "Own children Older\n(compared to no children)" = "PAOC_labelOlder children",
                 "Own children Younger\n(compared to no children)" = "PAOC_labelYounger children",
                "Interaction:\nBoth Children and log-transformed income" = "log(PINCP):PAOC_labelBoth children",
                "Interaction:\nOlder Children and log-transformed income"="log(PINCP):PAOC_labelOlder children",
                "Interaction:\nYounger Children and log-transformed income"="log(PINCP):PAOC_labelYounger children",
                "Interaction:\nDivorced and Both Children" = "marriage_statusDivorced:PAOC_labelBoth children",
                "Interaction:\nMarried and Both Children" = "marriage_statusMarried:PAOC_labelBoth children",
                "Interaction:\nSeparated and Both Children" = "marriage_statusSeparated:PAOC_labelBoth children",
                "Interaction:\nWidowed and Both Children" = "marriage_statusWidowed:PAOC_labelBoth children",
                "Interaction:\nDivorced and Older Children" = "marriage_statusDivorced:PAOC_labelOlder children",
                "Interaction:\nMarried and Older Children" = "marriage_statusMarried:PAOC_labelOlder children",
                "Interaction:\nSeparated and Older Children" = "marriage_statusSeparated:PAOC_labelOlder children",
                "Interaction:\nWidowed and Older Children" = "marriage_statusWidowed:PAOC_labelOlder children",
                "Interaction:\nDivorced and Younger Children" = "marriage_statusDivorced:PAOC_labelYounger children",
                "Interaction:\nMarried and Younger Children" = "marriage_statusMarried:PAOC_labelYounger children",
                "Interaction:\nSeparated and Younger Children" = "marriage_statusSeparated:PAOC_labelYounger children",
                "Interaction:\nSeparated and Younger Children" = "marriage_statusWidowed:PAOC_labelYounger children")

export_summs(model1, model3, 
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial model", "Preferred model"),
             coefs = coeff_names)
```

```{r}
coeff_desc <- c("Divorced\n(compared to never married)" = 
                  "marriage_statusDivorced",
                 "Married\n(compared to never married)" = 
                  "marriage_statusMarried",
                 "Separated\n(compared to never married)" = 
                  "marriage_statusSeparated",
                 "Widowed\n(compared to never married)" = 
                  "marriage_statusWidowed",
                "Having both children AND doubling income" = 
                  "log(PINCP):PAOC_labelBothchildren",
                 "Having older children AND doubling income" = 
                  "log(PINCP):PAOC_labelOlderchildren",
                "Having younger children AND doubling income" = 
                  "log(PINCP):PAOC_labelYoungerchildren",
                 "Being divorced AND having both children" = 
                         "marriage_statusDivorced:PAOC_labelBoth children",
                "Being married AND having both children" = 
                         "marriage_statusMarried:PAOC_labelBoth children",
                "Being separated AND having both children" = 
                         "marriage_statusSeparated:PAOC_labelBoth children",
                "Being widowed AND having both children" = 
                         "marriage_statusWidowed:PAOC_labelBoth children",
                 "Being divorced AND having Older children" = 
                         "marriage_statusDivorced:PAOC_labelOlder children",
                "Being married AND having older children" = 
                         "marriage_statusMarried:PAOC_labelOlder children",
                "Being separated AND having older children" = 
                         "marriage_statusSeparated:PAOC_labelOlder children",
                "Being widowed AND having older children" = 
                         "marriage_statusWidowed:PAOC_labelOlder children",
                 "Being divorced AND having younger children" = 
                         "marriage_statusDivorced:PAOC_labelYounger children",
                "Being married AND having younger children" = 
                         "marriage_statusMarried:PAOC_labelYounger children",
                "Being separated AND having younger children" = 
                         "marriage_statusSeparated:PAOC_labelYounger children",
                "Being widowed AND having younger children" = 
                         "marriage_statusWidowed:PAOC_labelYounger children")

plot_coefs(model3, 
           coefs = coeff_desc,
           plot.distributions = TRUE,
           rescale.distributions = TRUE) +
  scale_x_continuous(name = "Effect on women in WA receiving public assistance income- past 12 months")
```

```{r} 
interact_plot(model3, pred = PINCP, modx = PAOC_label, interval = TRUE) +
  scale_x_continuous(name = "Annual income (thousands)",
                     limits = c(0, 500000),
                     breaks = breaks <- seq(0, 500000, by = 50000),
                     labels = paste("$", 
                                    prettyNum(breaks/1000, big.mark = "'"),
                                    sep = "")) +
  scale_y_continuous(name = "Age of children at home",
                     breaks = seq(0, 0, by = 0)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```

```{r}
interact_plot(model3, pred = PINCP, modx = PAOC_label, interval = TRUE) +
  scale_x_continuous(name = "Income (thousands)") +
  scale_y_continuous(name = "Public Assistance received (thousands)",
                     breaks = seq(0, 15000, by = 5000)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```

```{r}
interact_plot(model3, pred = PINCP, modx = marriage_status, interval = TRUE) +
  scale_x_continuous(name = "Income (thousands)") +
  scale_y_continuous(name = "Public Assistance received (thousands)",
                     breaks = seq(0, 15000, by = 5000)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```


```{r} 
interact_plot(model3, pred = PINCP, modx = marriage_status, interval = TRUE) +
  scale_x_continuous(name = "Annual income (thousands)",
                     limits = c(0, 500000),
                     breaks = breaks <- seq(0, 500000, by = 50000),
                     labels = paste("$", 
                                    prettyNum(breaks/1000, big.mark = "'"),
                                    sep = "")) +
  scale_y_continuous(name = "Marriage status",
                     breaks = seq(0, 0, by = 0)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```

```{r}
cat_plot(model3, pred = marriage_status, modx = PAOC_label, interval = TRUE) +
 scale_x_discrete(name ="Marriage Status",
                    labels = c("Never Married", "Divorced", "Married",
                               "Separated", "Widowed")) +
  scale_y_continuous(name = "Public Assistance Income",
                     breaks = seq(0, 15000, by = 5000)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```






