---
title: "Quant_Assignment3"
author: "Wanjiku Ngare"
date: "10/1/2020"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
person_data <- read_csv("people.csv") %>%
  mutate(PAOC_label = case_when(
    PAOC_label== "Females with own children 6 to 17 years only"~"Older Children",
    PAOC_label== "Females with own children under 6 years and 6 to 17 years" ~ "All Children",
    PAOC_label=="Females with own children under 6 years only"~"Younger Children"))%>%
   
  mutate(year_married = case_when(
    MARHYP > 1935 & MARHYP < 1951 ~ "1936-1950",

    MARHYP > 1950 & MARHYP < 1971 ~ "1951-1970",

    MARHYP > 1970 & MARHYP < 1991 ~ "1971-1990",

    MARHYP > 1990 & MARHYP < 2011 ~ "1991-2010",

    MARHYP > 2010 & MARHYP < 2019 ~ "2011-2018"))%>%
  
select(year_married, PAOC_label, SEX_label, PAP, PINCP) 
```

```{r}
correlation <- cor.test(person_data$PINCP, person_data$PAP)
options(scipen = 999)
correlation
```

```{r}
ggplot(person_data, aes(x = PINCP, y = PAP)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Income",
  limits = c(0, 200000),
                     breaks = seq(0, 200000, by = 25000),  
   labels = paste("$",
     prettyNum(seq(0, 200000, by = 25000),
                                              big.mark = ",")))+
  scale_y_continuous(name = "Public Assistance", 
                     breaks = seq(0, 25000, by = 2000),
                     labels = paste("$", 
                                    prettyNum(seq(0, 25000, by = 2000),
                                              big.mark = ","))) +
  annotate(geom = "text", x = 5000, y = 21000, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1], digits = 2), 
                         "to",
                         prettyNum(correlation$conf.int[2], digits = 2)),
           hjust = 0)
```
#The above is a Pearson's Correlation test between the variables: Public Assistance (PAP) and Income (PINCP) of women in Seattle 'with own" children between the ages of 6 and 17 years only, under 6 years only, and under 6 years and 6 to 17 years. The test shows a low p-value of 0.00000000001004 suggesting, and a high correlation of 0.4678468 between the two values. In layman's  terms, the low p-value suggests that there's a very small chance that income doesn't impact public assistance.

```{r}
anova <- aov(PINCP ~ PAOC_label, data = person_data)

summary(anova)
```

#This suggest that with a 95% confidence interval, there is a significant association between income and number of own children for women in Seattle. 

```{r}
differences <- TukeyHSD(anova)

as_tibble(cbind(pair = row.names(differences$PAOC_label),
                differences$PAOC_label))
```

#Anova Test between number of own children a female person in Seattle has, and their income
```{r}
ggplot(person_data, aes(x = PAOC_label, y = PINCP)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Number of Own Children") +
  scale_y_continuous(name = "Annual Income", 
                     breaks = seq(0, 800000, by = 50000),
                     labels = paste("$", 
                                    prettyNum(seq(0, 800000, by = 50000),
                                              big.mark = ","))) 
```

#Chisquare test between number of own children a female in Seattle has, and years married 
#I was unable to run the chi.square test because I kept getting this error:
#Error in chisq.test(person_data$PAOC_label, person_data$years_married == : 'x' and 'y' must have the same length
























