d---
title: "Week 1"
author: "Wanjiku Ngare"
date: "9/13/2020"
output: html_document
---

```{r load libraries}
library(tidycensus)
library(tidyverse)

person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```

## ACLS 2018 Data - The impact of partnership and income on public assistance seeking behavior and attainement of people in the state of Washington who have children 

After looking through the available variables in 'person_vars_2018' , I've decided to complete a person-level analysis using the following 5 Variables:

1. Income (PINCP) (continuous)
2. Presence and age of own children (PAOC) (categorical)
3. Sex (SEX) (categorical)
4. Year last married (MARHYP) (continuous)
5. Public assistance income past 12 months (PAP) (continuous)

And I want my survey to include all people in the state of Washington who have children of their own (everyone with a value greater than zero for presence and age of children of their own). 

```{r load person-level data, results = 'hide'}
person_data <- get_pums(variables = c("PAOC", 
                                      "SEX", 
                                      "PINCP", 
                                      "MARHYP", 
                                      "PAP"),
                        state = "WA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(PAOC > 0) %>%
  select(PAOC_label, SEX_label, PINCP, MARHYP, PAP)
```

```{r show person-level data}
person_data <- person_data[person_data$PAOC_label != "N/A (male/female under 16 years old/GQ)", ] 
person_data <- person_data[person_data$PAOC_label != "Females with no own children", ] 
unique(person_data$PAOC_label)
```

### Description of  data

There are 76225 total observations for 5 variables (PAOC, SEX, PINCP, MARHYP, PAP - see above descriptive label). However, of the variables we want to observe for this analysis, there are 7294. The goal of the analysis is to understand if income and having a partner or co-parent(s) impacts if and how much people who are parents access public assistance income. Partnership or ca-parenting is indicated by 'Year Last Married' for the purposes of the census data which does not collect data about other forms of partnership or co-parenting.  
